### 2015-08-10 A4/writeup.tex
Add .gitignore and writeup.

@@

>>>>

\usepackage{graphicx}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.75\textwidth]{image.png}
\caption{Data from timing threaded versus process programs. This is strange behavior. For this range of numbers, 100 million, adding more processes makes the situation worse once you have more than eight processes or one thread. This probably shows a problem in my implementation, although for reasons described below, this level of work might not actually benefit from more parallelization. The main thread calls new threads every time it gets a timeslice. However if the threads are completing in between main() timeslices, then more threads doesn't mean more speed..}
\end{figure}
